### 2021-05-02 Paper/Main.tex
Updates from Overleaf

\section{Appendix}
%take these when needed
\begin{center}
    \paperspacingnarrow
    \input{Code/data/desc1}\\
    \textbf{Table 1: EXPLAIN THE TABLE!!!}
    \paperspacingwide
\end{center}

\begin{center}
    \paperspacingnarrow 
    \input{Code/data/size_summary_stat_size}\\
    \textbf{Table 2:} This table shows the mean results by decile before any regressions\\
    \paperspacingwide
 \end{center}
\vspace{1cm}

\begin{center}
    \paperspacingnarrow
    \input{Code/data/FF_pass_2}\\
    \textbf{Table 4:} second pass results for the size and beta decile portfolios\\
    \paperspacingwide
\end{center}

@@

\begin{center}
    \paperspacingnarrow
\input{Code/data/All_Industry_FF_pass_2_past_2018}\\
\textbf{Table XX:} SIC top 10\% minus bottom 10\%
    \paperspacingwide
\end{center}
\clearpage
\restoregeometry

>>>>

\section{Appendix}
%take these when needed

@@

\begin{center}
    \paperspacingnarrow
\input{Code/data/All_Industry_FF_pass_2_past_2018}\\
\textbf{Table XX:} SIC top 10\% minus bottom 10\% 2018-2020
    \paperspacingwide
\end{center}
\clearpage
\restoregeometry

### 2021-05-02 Paper/Results.tex
Updates from Overleaf

When considering the second phase of the two-pass sort for the beta decile portfolios, the similarities to the size decile continue wherein market returns, SMB CMA and EMP exhibit positive risk premia. The other two factors remain statistically insignificant, and the MHL factor changed signs and now has a positive relationship. The EMP coefficient indicates that a one-unit change in beta would result in a 7.36\% change in returns for a high ESG company. This result is slightly smaller than the result from the size portfolio but still demonstrates a statistical relationship in the same order of magnitude. The model is also a good fit with an $R^2$ value of 86.0%

@@

Moving on to the second stage of the analysis, I constructed an ESG factor out of the MSCI ESG ratings to capture a more holistic view of ESG risk. I created this factor by taking the top 10\% of MSCI EGS rated companies and subtracted them from the bottom 10\% of firms rated by the MSCI. I repeated the methodology above for the regression analysis. I  regressed two sets of two-pass regression analyses one on beta-sized portfolios and another on size-based portfolios. In the first pass results from the new factor, the beta portfolio demonstrated a decrease in sensitivity as the betas grew; however, the size-based portfolios did not experience any real pattern governing the decile and the sensitivity. In the case of the size-based portfolios, some of the sensitivity figures were positive while others were negative. Table 4 represents a second stage two-pass sort regression output from this table it is clear that

\begin{center}
    \paperspacingnarrow
\input{Code/data/All_Industry_FF_pass_2}\\
\textbf{Table 4:} SIC top 10\% minus bottom 10\%
    \paperspacingwide
\end{center}

>>>>

When considering the second phase of the two-pass sort for the beta decile portfolios, the similarities to the size decile continue wherein market returns, SMB, CMA, and EMP exhibit positive risk premia. The other two factors remain statistically insignificant, and the MHL factor changed signs and now has a positive relationship. The EMP coefficient indicates that a one-unit change in beta would result in a 7.36\% change in returns for a high ESG company. This result is slightly smaller than the result from the size portfolio but still demonstrates a statistical relationship in the same order of magnitude. The model is also a good fit with an $R^2$ value of 86.0\%. With the baseline analysis proving that there is a relationship between ESG and excess marker returns, I will provide an investigation of the robustness in section \ref{Robustness} by first comparing the results of the two-pass sort with the EGS factor to the same analysis without the factor. Next, I will investigate time-related relationships between ESG and excess returns by implementing a dummy variable for the year and repeating the two-pass sort methodology.

@@

Moving on to the second stage of the analysis, I constructed an ESG factor out of the MSCI ESG ratings to capture a more holistic view of ESG risk. I created this factor by taking the top 10\% of MSCI EGS rated companies and subtracted them from the bottom 10\% of firms rated by the MSCI. I repeated the methodology above for the regression analysis. I  regressed two sets of two-pass regression analyses, one on beta-sized portfolios and another on size-based portfolios. In the first pass results for the MSCI factor, the beta portfolio demonstrated a decrease in sensitivity as the betas grew; however, the size-based portfolios did not experience any real pattern governing the decile and the sensitivity. In the case of the size-based portfolios, some of the sensitivity figures were positive while others were negative. Table 5 represents a second stage two-pass sort regression output. Similar to the regression in the first stage of the analysis, the market return, CMA, SMB remain statistically significant; however, only the size-based portfolios demonstrate a statistically significant coefficient for the ESG factor.  The EMP ESG factor coefficient can be interpreted as a negative relationship between ESG and excess return wherein a one beta unit increase in ESG results in a decrease of 2\% in excess returns. One limitation of the MSCI data is it only represents a snapshot in ESG rating data; that is, the MSCI data is only the most recent ESG performance and does not account for changes in ESG performance. As such, a company that used to be a  poor ESG and has improved to a strong ESG company will only be categorized as a strong ESG company which will not accurately address the ESG performance.  As such, in section \ref{Robustness} I will address this by shrinking the time frame to see if the coefficients increase in their significance. Further,  to address additional concerns of robustness, I will run another two-pass sort to isolate the SIC industry-specific ESG factor and determine if there are ESG related excess returns that are greater in some industries than others.

\begin{center}
    \paperspacingnarrow
    \input{Code/data/All_Industry_FF_pass_2}\\
    \textbf{Table 5:} SIC top 10\% minus bottom 10\%
    \paperspacingwide
\end{center}
